```{r setup1, include= FALSE}
knitr::opts_chunk$set(
    comment = NA,
    echo    = TRUE,
    error   = TRUE,
    results = 'markup'
)
```

```{r setup2, results= 'hide', message= FALSE, warning= FALSE}
#rm(list= ls())

library(rms)
library(data.table)
```

```{r makedat}
N <- 100
dat <- data.table(
    x1 = rnorm(N), 
    x2 = rnorm(N),
    exposed = rbinom(N, 1, 0.7)
)

dat[1:15, x1 := NA]
dat[, x1 := impute(x1)]
dat[, x1.is.imputed := is.imputed(x1)]

dd <- datadist(dat)
options(datadist = 'dd')

describe(dat)
```

What I would like to do is this:
```{r fit1glm}
fit1glm <- glm(exposed ~ x1 + x2 + is.imputed(x1), 
    family= 'binomial', data= dat)
fit1glm
```

It works with glm (above), but not with lrm:
```{r fit1lrm}
fit1lrm <- lrm(exposed ~ x1 + x2 + is.imputed(x1), data= dat)
```

I think the problem has to do with the names the terms are given. In the glm() model fit above the terms get the following names:
```{r glmnames}
names(coef(fit1glm))
```

But if we use is.imputed() with lrm(), the is.imputed(x1) term gets called "x1", so we can't use x1 and is.imputed(x1) in the same model:
```{r fit2lrm}
fit2lrm <- lrm(exposed ~ x2 + is.imputed(x1), data= dat)
fit2lrm
```
lrm() works fine if we give the is.imputed() term a different name in the dataset:
```{r fit3lrm}
fit3lrm <- lrm(exposed ~ x1 + x2 + x1.is.imputed, data= dat)
fit3lrm
```

